Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-11-10 Ben_Manuscripts/structure_paper/Outline.tex
New figures and more revision

  %BJC: Figure here showing previous level of detail compared to atomistic level of detail
  \begin{figure}[ht]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{nanopore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
  \caption{(a) Our previous understanding of the pore structure allows us to speculate
	   about separation behavior. (b) A detailed molecular model will allow us to
	   directly observe solute transport}~\label{fig:detail}
  \end{figure}

@@

   (4) Is it necessary to include any water in order to appropriately model the 
   Col\testsubscript{h} phase?
   \begin{itemize}
	\item While the Col\textsubscript{h} phase is described as dry, it is 
	possible that small amounts of ambient water may be leached into the system.
	\item The hydrogen bonding network formed by the water may play a role 
        in structuring the pore.
	\item We can use simulated X-ray diffraction patterns to see if there is
        any meaningful structural difference between a "dry" and "wet" system
   \end{itemize}

@@

  \begin{figure}[!ht]
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
  \end{figure}

@@

  \begin{figure}[!ht]
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
        %       \vspace{12mm}
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \raisebox{.2\textwidth}{%
                \includegraphics[width=\linewidth]{WAXS_annotated.png}
                }
                \caption{}\label{fig:WAXS}
        \end{subfigure}
        \caption{(a) 1D small angle X-ray scattering indicates hexagonal packing of
	pores as well as the spacing between pores (b) 2D wide angle X-ray scattering 
	gives details about repeating features less than 1 nanometer apart}\label{fig:SWAXS}
  \end{figure}

@@

  \begin{figure}[ht]
 	\centering
 	\includegraphics[width=\textwidth]{pore_radius_illustration.png}
	\caption{The pore radius of the initial configuration is defined using the 
        carboxylate carbon as a reference}~\label{fig:pore_radius_illustration}
  \end{figure}

@@

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

@@

  To discern the composition of the monomer layers, addressing (1), we ran
  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  \begin{itemize}
        \item We created systems in both the parallel displaced and sandwiched configurations
	\item All systems were prepared according to the dry equilibration procedure
        \item All systems are stable after 400 ns of simulation.  
        \item Table ~\ref{table:p2p} shows the pore spacing for all systems tested.
        \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
        that is most consistent with the experimental value of 4.12 nm derived from
        SAXS measurements (Figure~\ref{fig:SAXS}).
        \item The remainder of this discussion will focus on the analysis of systems
        built with 5 monomers per layer.
  \end{itemize}

@@

  \begin{figure}[!ht]
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf5layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf5offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
        \caption{Pair distribution functions of aromatic carbons for the
        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
        parallel displaced configurations. Clear periodic maxima in the
        $z$ probability density indicate distinct layers. The magnitude
        of the spikes with respect to the average suggest that the 5
        monomer per layer, sandwiched configuration possesses a higher
        degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.72 \pm 0.04$ & $3.84 \pm 0.02$ \\  % done
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.69 \pm 0.04$ & $4.72 \pm 0.03$ \\
  7 & $4.66 \pm 0.02$ & $4.82 \pm 0.03$ \\  % done
  8 & $5.00 \pm 0.04$ & $5.33 \pm 0.02$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing (given in nm) of the model increases as
  number of monomers in each layer increases. The pore spacing of a system
  starting in the sandwiched configuration is systematically lower than 
  that started in an offset configuration. Systems built with 5 monomers
  per layer in a parallel displaced configuration result in a pore spacing
  closest to the experimental 4.12 nm}
  \label{table:p2p} 
  \end{table}

@@

  \begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
  indicates an average tilt angle near 7\degree which is far from the 37\degree tilt angle 
  previously used to explain R-spots}~\label{fig:tilt}
  \end{figure}

@@

  \begin{figure}[ht]
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:rz_layered}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:test}
		\end{subfigure}
	\end{subfigure}
  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
  same peaks are visible when the 2D simulated diffraction data is radially integrate in the R-alkanes region,
  (b) and (d) respectively.}~\label{fig:tail_packing}
  \end{figure}

@@

  \begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
	\label{fig:solvation}
  \end{figure}

@@

  The calculated values of ionic conductivity are higher than experiment by an
  order of magnitude. 
  \begin{itemize}
	\item One can justify the reason for this result by considering the 
	real system studied experimentally
	\item The ionic conductivity measurement to which we are comparing was done
	on a \SI{80}{\micro\metre} thick film, nearly 10,000 times thicker than 
        our simulated system. 
	\item The thick film likely has defects leading to non-continuous pores and
	imperfect alignment.
	\item The 2D SAXS pattern highlights the small degree of tortuosity present
	in the system  % BJC: insert 2D SAXS data -- maybe azimuthal distribution
	\item It has been shown that there is a large dependence of Ionic conductivity
	on the alignment of the pores
	\item The ionic conductivity of an unaligned film is 85 times lower than that
	of a nearly aligned film referenced here  % BJC: reproduce figure from 2014
	\item It is not unreasonable that a thin, perfectly aligned film would have 
	a value of ionic conductivity in agreement with our model
  \end{itemize}

@@

  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
  the OP basin.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
  	\item There is an even distribution of crosslinks between same monomer tails, 
	between monomers in the same pore and between monomers in different pores 
	including periodic boundaries.
	\item We reach 95 \% conversion of terminal vinyl groups
	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
	crosslinked
	\item Major features are still present in the X-ray diffraction
	\item The ionic conductivity is higher/lower in the crosslinked system
  \end{itemize}
  %BJC: THe following figure will be replaced with one representative of the new
  % data I am  collecting above.
  \begin{figure}[!ht]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}

@@

  We have used a detailed molecular model of the Col\textsubscript{h} phase formed by NA-GA3C11
  in order to study the nanoscopic structure.
  \begin{itemize}
  	\item While there have been efforts to model formation of various liquid crystalline 
	phases with molecular dynamics, to our knowledge there have been no studies which 
	attempt to examine their structure with the same level of detail presented here.
	\item We have confirmed that monomers stay partitioned in layers.
	\item We were able to deduce that layers are composed of 5 monomers.
	\item We have identified two metastable basins which each consist of a set of 
	similar monomer configurations characterized by the degree of order in the pore region.
	\item We verified that the basins are not separate phases.
	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
	membrane strucure. 
	\item Simulated diffration patterns generated from MD trajectories suggest that
	the offset configuration produces a structure with the closest match to experiment. 
	\item Even though our model only answers these questions for a system created by 
	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
	little extra effort. 
  \end{itemize}

>>>>

  %BJC: Figure here showing previous level of detail compared to atomistic level of detail
  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
  \caption{(a) Our previous understanding of the pore structure allows us to speculate
	   about separation behavior. (b) A detailed molecular model will allow us to
	   directly observe solute transport}~\label{fig:detail}
  \end{figure}

@@

   (4) Is it necessary to include any water in order to appropriately model the 
   Col\textsubscript{h} phase?
   \begin{itemize}
	\item While the Col\textsubscript{h} phase is described as dry, it is 
	possible that small amounts of ambient water may be leached into the system.
	\item The hydrogen bonding network formed by the water may play a role 
        in structuring the pore.
	\item We can use simulated X-ray diffraction patterns to see if there is
        any meaningful structural difference between a "dry" and "wet" system
   \end{itemize}

@@

  \begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
  \end{figure}

@@

  \begin{figure}
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
        %       \vspace{12mm}
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \raisebox{.2\textwidth}{%
                \includegraphics[width=\linewidth]{WAXS_annotated.png}
                }
                \caption{}\label{fig:WAXS}
        \end{subfigure}
        \caption{(a) 1D small angle X-ray scattering indicates hexagonal packing of
	pores as well as the spacing between pores (b) 2D wide angle X-ray scattering 
	gives details about repeating features less than 1 nanometer apart}\label{fig:SWAXS}
  \end{figure}

@@

  \begin{figure}
 	\centering
 	\includegraphics[width=\textwidth]{pore_radius_illustration.png}
	\caption{The pore radius of the initial configuration is defined using the 
        carboxylate carbon as a reference}~\label{fig:pore_radius_illustration}
  \end{figure}

@@

  \begin{figure}
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

@@

  To discern the composition of the monomer layers, addressing (1), we ran
  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  \begin{itemize}
        \item We created systems in both the parallel displaced and sandwiched configurations
	\item All systems were prepared according to the dry equilibration procedure
        \item All systems are stable after 400 ns of simulation.  
        \item Table ~\ref{fig:p2p} shows the pore spacing for all systems tested.
        \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
        that is most consistent with the experimental value of 4.12 nm derived from
        SAXS measurements (Figure~\ref{fig:SAXS}).
        \item The remainder of this discussion will focus on the analysis of systems
        built with 5 monomers per layer.
  \end{itemize}

@@

  \begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf5layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf5offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
        \caption{Pair distribution functions of aromatic carbons for the
        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
        parallel displaced configurations. Clear periodic maxima in the
        $z$ probability density indicate distinct layers. The magnitude
        of the spikes with respect to the average suggest that the 5
        monomer per layer, sandwiched configuration possesses a higher
        degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

@@

  \begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{p2p.png}
	\caption{The pore spacing (given in nm) of the model increases as
	number of monomers in each layer increases. The pore spacing of a system
	starting in the sandwiched configuration is systematically lower than 
	that started in an offset configuration. Systems built with 5 monomers
	per layer in a parallel displaced configuration result in a pore spacing
	closest to the experimental 4.12 nm}~\label{fig:p2p}
  \end{figure}

%  \begin{table}[h]
%  \centering
%  \begin{tabular}{ccc}
%  \toprule
%  		   & \multicolumn{2}{c}{Starting Configuration} \\
%  \hline
%  Monomers per layer & Sandwiched & Parallel Displaced \\
%  \midrule
%  4 & $3.72 \pm 0.04$ & $3.84 \pm 0.02$ \\  % done
%  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
%  6 & $4.69 \pm 0.04$ & $4.72 \pm 0.03$ \\
%  7 & $4.66 \pm 0.02$ & $4.82 \pm 0.03$ \\  % done
%  8 & $5.00 \pm 0.04$ & $5.33 \pm 0.02$ \\
%  \bottomrule
%  \end{tabular}
%  \caption{The pore spacing (given in nm) of the model increases as
%  number of monomers in each layer increases. The pore spacing of a system
%  starting in the sandwiched configuration is systematically lower than 
%  that started in an offset configuration. Systems built with 5 monomers
%  per layer in a parallel displaced configuration result in a pore spacing
%  closest to the experimental 4.12 nm}
%  \label{table:p2p} 
%  \end{table}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
  indicates an average tilt angle near 7\degree which is far from the 37\degree tilt angle 
  previously used to explain R-spots}~\label{fig:tilt}
  \end{figure}

@@

  \begin{figure}
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:rz_layered}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:test}
		\end{subfigure}
	\end{subfigure}
  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
  same peaks are visible when the 2D simulated diffraction data is radially integrate in the R-alkanes region,
  (b) and (d) respectively.}~\label{fig:tail_packing}
  \end{figure}

@@

  \begin{figure}
	\centering
	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
	\label{fig:solvation}
  \end{figure}

@@

  The calculated values of ionic conductivity are higher than experiment by an
  order of magnitude. 
  \begin{itemize}
	\item One can justify the reason for this result by considering the 
	real system studied experimentally
	\item The ionic conductivity measurement to which we are comparing was done
	on a \SI{80}{\micro\metre} thick film, nearly 10,000 times thicker than 
        our simulated system. 
	\item The thick film likely has defects leading to non-contiguous pores and
	imperfect alignment.
	\item The 2D SAXS pattern shows the small degree of tortuosity present
	in the system (~\ref{fig:2DSAXS})  % BJC: insert 2D SAXS data -- maybe azimuthal distribution
	\item It has been shown that there is a large dependence of Ionic conductivity
	on the alignment of the pores
	\item The ionic conductivity of an unaligned film is 85 times lower than that
	of a nearly aligned film referenced here  % BJC: reproduce figure from 2014
	\item It is not unreasonable that a thin, perfectly aligned film would have 
	a value of ionic conductivity in agreement with our model
  \end{itemize}

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{2D-SAXS_cropped.png}
  % BJC: I will add axes with q values if this ends up in the final draft
  % BJC: I'll also see what I can do about all the white speckles
  \caption{The experimental two dimensional SAXS pattern exhibits reflections
  resulting from highly aligned pore regions. A perfectly aligned system 
  would exhibit sharp dots at the same locations of the refelctions shown. 
  An isotropically aligned system the refelctions would appear as 
  rings centered about the origin}~\label{fig:2DSAXS}
  \end{figure}

@@

  We applied the crosslinking algorithm to the equilibrated parallel-displaced  
  configuration with 5 monomers per layer.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
  	\item There is an even distribution of crosslinks between same monomer tails, 
	between monomers in the same pore and between monomers in different pores 
	including periodic boundaries.  % BJC: might leave this detail in the supplemental
	\item We reach 95 \% conversion of terminal vinyl groups % BJC: we'll see
	\item The distance between pores shrinks by 1 \angstrom~ after the system is 
	crosslinked  % probably smaller
	\item We simulated the crosslinked simulations in the NPT ensemble for 100 ns
	\item Major features are still present in the X-ray diffraction ~\ref{fig:rzplot_xlink} % BJC: maybe
	\item The ionic conductivity is higher/lower in the crosslinked system ~\ref{fig:ic_xlink} % BJC: Nernst-Einstein is lower. Need a longer simulation to check Collective-Diffusion 
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[widht=\textwidth]{rzplot_xlink.png}
	\caption{}~\label{fig:rzplot_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{ic_xlink.png}
	\caption{}~\label{fig:ic_xlink}
  \end{subfigure}
  \caption{(a) Reflections produced by the crosslinked configuration fade relative
  to the uncrosslinked system. The colorbar shown is the same used for the uncrosslinked
  system. (b) The ionic conductivity is smaller relative to the uncrosslinked system, but
  still much larger than the experimental value}~\label{fig:xlink}
  \end{figure}

%  \begin{figure}
%	\centering
%	\begin{subfigure}{0.31\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
%		\caption{}\label{fig:p2p_diagram}
%	\end{subfigure}
%		\begin{subfigure}{0.31\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
%		\caption{}\label{fig:no_xlink_p2p}
%	\end{subfigure}
%		\begin{subfigure}{0.31\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{xlink_p2p.png}
%		\caption{}\label{fig:xlink_p2p}
%	\end{subfigure}
%	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
%	Each numbered circle represents a pore. Distances are measured along each of the 
%	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
%	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
%	individual pores in the crosslinked system are stable relative to the uncrosslinked
%	system}\label{fig:xlink}
%  \end{figure}

@@

  We have used a detailed molecular model of the Col\textsubscript{h} phase formed by NA-GA3C11
  in order to study the nanoscopic structure.
  \begin{itemize}
  	\item While there have been efforts to model formation of various liquid crystalline 
	phases with molecular dynamics, to our knowledge there have been no studies which 
	attempt to examine their structure with the same level of detail presented here.
	\item We were able to deduce that layers are composed of 5 monomers 
        \item We have confirmed that monomers stay partitioned in layers.
	\item We have explored the affect of two different $\pi$-$\pi$ stacking modes on the equilibrated
	membrane strucure. 
	\item Simulated diffration patterns generated from MD trajectories suggest that
	the parallel-displaced configuration produces a structure with the closest match to experiment.
	\item Finally, water is not needed to maintain membrane structure 
	\item Now that we have a good idea of what the membrane structure should look like, we will
	evaluate transport of various solutes within the system. 
	\item We will apply the knowledge gained from this study in order to 
        suggest improvements to the existing system as well as to evaluate new
	unsynthesized LLC systems.
%	\item Even though our model only answers these questions for a system created by 
%	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
%	little extra effort. 
  \end{itemize}
